Calculating life expectancy and exploring missingness

### 2016-10-28 Code/1_Explore_Data_v2.Rmd

>>>>

```{r investigate_problem}

list.cod.decomp.tables[[which(paired.ids$StateYearRaceSexBlack == "Washington DC.2013.Black.Male")]]
#index == 2115 fyi

View(dat.clean[dat.clean$State2 == "Washington DC" & dat.clean$Year3 == 2013 & dat.clean$Sex2 == "Male",])
#see the problem is that white males at 1-4 years have no deaths and prop deaths due to each cod == NaN.

list.age.decomp.tables[[which(paired.ids$StateYearRaceSexBlack == "Washington DC.2013.Black.Male")]]

View(list.life.tables[[which(non.zero.stratums == "Washington DC.2013.White.Male")]])
